Cloud Manufacturing xxx from a ecosystem view

### 2016-03-23 background.tex
添系统框架参考图
test the figures

\subsection{Cloud Manufacturing Ecosystem} % (fold)
\label{sub:cloud_manufacturing_ecosystem}

>>>>

\subsection{Cloud Manufacturing Ecosystem} % (fold)
\label{sub:cloud_manufacturing_ecosystem}
As an application of Networked Manufacturing, Cloud Mfg ...
\begin{figure}
\includegraphics[scale = .6, trim = 0 15 0 0]{Cloud_Mfg_Structure.pdf}
\caption{Cloud Manufacturing Architecture with Main Flows}
\label{fig:structure}
\end{figure}

As shown in \autoref{fig:structure}, the architecture of Cloud Mfg is mainly comprised by three parts, namely User, Platform and Physical Base, some of whose subparts are connected by (material or information) flows. With the supplementary illustration in \autoref{fig:supplementary}

\begin{figure}[!htpd]
\includegraphics[scale = .6, trim = 0 15 0 0]{supplementary.pdf}
\caption{Supplementay Illustration of \autoref{fig:structure}}
\label{fig:supplementary}
\end{figure}
